---
title: "A Crafty Crawl"
output: html_notebook
---

```{r, include=FALSE}
setwd("~/Desktop/SomethingWithNumbers/CraftBeerCrawl")

library(sp)
library(tspmeta)
library(tidyverse)
library(leaflet)
library(googleway)
library(RCurl)
library(RJSONIO)
library(dplyr)
library(gmapsdistance)


source("~/Desktop/SomethingWithNumbers/key.R")

```

# Background 
Earlier this year, Beer Cartel ran their annual
[Beer Cartel Australian Craft Beer Survey](https://www.beercartel.com.au/blog/2017-australian-craft-beer-survey-results/).  I thought'd be fun to find the most optimal craft beer crawl in each captial city - with a mix of breweries and bars/pubs. Over 17,000 craft beer drinkers took part in the survey, and to be the 'best' a bar/pub made had to achieve at least 1% of the vote for it's state.  I've also included breweries (as so many of them have on site taprooms - TODO: Check this is a good assumption)  and if it was in the survey, I've considered it 'craft' (contentious I know!). 

# The Data
```{r, eval=FALSE, include=FALSE}
# load data
Breweries <- read_csv("Data/BestBrewery.csv")
QldBar <- read_csv("Data/QldBar.csv")
NswBar <- read_csv("Data/NswBar.csv")
ActBar <- read_csv("Data/ActBar.csv")
VicBar <- read_csv("Data/VicBar.csv")
TasBar <- read_csv("Data/TasBar.csv")
SABar <- read_csv("Data/SaBar.csv")
WABar <- read_csv("Data/WaBar.csv")

```
```{r}
Breweries 
QldBar 
NswBar 
ActBar 
VicBar 
TasBar 
SABar
WABar

```

# Google
Before passing to the GooglePlaces API, the data will need a bit of a tidy up.
```{r, eval=FALSE, include=FALSE}
# Add in State, Country to help googlePlaces along
Breweries$State <- rep("Australia", length(Breweries$Brewery))
QldBar$State <- rep("QLD", length(QldBar$Bar))
NswBar$State <- rep("NSW", length(NswBar$Bar))
ActBar$State <- rep("ACT", length(ActBar$Bar))
VicBar$State <- rep("VIC", length(VicBar$Bar))
TasBar$State <- rep("TAS", length(TasBar$Bar))
SABar$State <- rep("SA", length(SABar$Bar))
WABar$State <- rep("WA", length(WABar$Bar))

# Combined
Bars <- rbind(QldBar, NswBar, ActBar, VicBar, TasBar, SABar, WABar)
Bars <- rename(Bars, Venue = Bar)
Bars$Type <- rep("Bar",length(Bars$Venue))
Breweries <- rename(Breweries, Venue = Brewery)
Breweries$Type <- rep("Brewery",length(Breweries$Venue))
CraftBeerAu <- rbind(Breweries, Bars)
colnames(CraftBeerAu)[colnames(CraftBeerAu)=="%"] <- "Percent Vote" # the dplyr way didn't work

# Add in State, Country to help googlePlaces along
CraftBeerAu$Search <- paste(CraftBeerAu$Venue, " in ", CraftBeerAu$State)

# Remove all punct (it messes with url)
# CraftBeerAu$Search <- gsub("[[:punct:]]", " ", CraftBeerAu$Search)
CraftBeerAu$Search <- gsub("/", " ", CraftBeerAu$Search)
CraftBeerAu$Search <- gsub("-", " ", CraftBeerAu$Search)
CraftBeerAu$Search <- gsub("\\(", " ", CraftBeerAu$Search)
CraftBeerAu$Search <- gsub("\\)", " ", CraftBeerAu$Search)
CraftBeerAu$Search <- gsub("\\_", "'", CraftBeerAu$Search)
CraftBeerAu$Search <- gsub("\\&", "and", CraftBeerAu$Search)
CraftBeerAu$Search <- gsub("\\+", "and", CraftBeerAu$Search)

```

# Gecoding with Googleway
```{r, eval=FALSE, include=FALSE}
# Sample to test 
Sample <- sample_n(Breweries, 5)

# Loop to get geocode
Places <- apply(CraftBeerAu, 1, function(x){
  google_places(search_string = list(x["Search"]),
                #place_type = "bar",
                key = PlacesKey)
})

# Extract the relevant bits 
name <- lapply(Places, function(x){ x[["results"]][["name"]][[1]] })
address <- lapply(Places, function(x){ x[["results"]][["formatted_address"]][[1]] })
lat <- lapply(Places, function(x){ x[["results"]][["geometry"]][["location"]][["lat"]][[1]] })
lng <- lapply(Places, function(x){ x[["results"]][["geometry"]][["location"]][["lng"]][[1]] })
status <- lapply(Places, function(x){ x[["status"]][[1]] })

# Unlsit and make a data frame
name <- unlist(name)
address <- unlist(address)
lat <- unlist(lat)
lng <- unlist(lng)
status <- unlist(status)

geocoded.CraftBeerAU <- data.frame(cbind(name, address, lat, lng), stringsAsFactors = FALSE)

geocoded.CraftBeerAU$lng <- as.numeric(geocoded.CraftBeerAU$lng)
geocoded.CraftBeerAU$lat <- as.numeric(geocoded.CraftBeerAU$lat)

# save(geocoded.CraftBeerAU, file = "Data/geocodedCraftBeerAu.rdata")

```

Googleway is nice, but I hate not being able to tell which rows weren't geocoded, so then:
```{r, eval=FALSE, include=FALSE}

# To access the GooglePlaces API
# Make a url like: https://maps.googleapis.com/maps/api/place/textsearch/json?query=123+main+street&key=YOUR_API_KEY
url <- function(search_text, return.call = "json") {
  root <- "https://maps.googleapis.com/maps/api/place/textsearch/"
  u <- paste(root, return.call, "?query=", search_text, "&key=", key, sep = "")
  return(URLencode(u))
}

DIYPlaces <- function(search_text,verbose=FALSE) {
  if(verbose) cat(search_text,"\n")
  u <- url(search_text)
  doc <- getURL(u)
  x <- fromJSON(doc,simplify = FALSE)
  if(x$status=="OK") {
    search_text <- search_text
    lat <- x$results[[1]]$geometry$location$lat
    lng <- x$results[[1]]$geometry$location$lng
    formatted_address  <- x$results[[1]]$formatted_address
    return(c(search_text, lat, lng, formatted_address))
  } else if(x$status=="ZERO_RESULTS") {
    return(c(paste0(search_text),"0","0","0"))
  } else if(x$status=="OVER_QUERY_LIMIT") {
    return(c(paste0(search_text),"limit","limit","limit"))
  } else {
    return(c(paste0(search_text),NA,NA,NA))
  }
}

# sample_diy <- sample_n(CraftBeerAu, 5)
# sample_search<- sample_diy$Search
# sample_geocoded <- ldply(sample_search, function(x) DIYPlaces(x))

# sample_diy <- sample_n(CraftBeerAu, 5)
search <- CraftBeerAu$Search
geocoded_search <- ldply(search, function(x) DIYPlaces(x))

names(geocoded_search)  <- c("Search", "lat", "lng", "Address")

geocoded_search <- as.data.frame(geocoded_search)

CraftBeerAu_geocoded <- left_join(CraftBeerAu, geocoded_search, by = "Search")
#save(CraftBeerAu_geocoded, file = "Data/DIYgeocodedCraftBeerAu.rdata")

CraftBeerAu_geocoded
```



```{r}
load("Data/DIYgeocodedCraftBeerAu.rdata")

```

# Not Found
There's 56 venues that were unable to be found.  Reviewing the list below, it looks to be made up of gypsy brewers (eg Doctor's Orders) or breweries not open to the public (Bodriggy) or faux craft brewers (Fat Yak).  There are two I'll manually fix - The Durham in Canberra (officially called The Durham Castle Arms) and Exit Brewing as they've opened a brew pub in Richmond. TODO: Check for others like these - maybe the places details api or use opening hours from the results).  Also the API has put The Terminus on the Vic/NSW border not it's usual spot in Fitzroy. 

```{r}
not_found <- CraftBeerAu_geocoded %>% filter(lat == 0 )
not_found
```

```{r}
# The Durham
# Green Square, 2 Jardine St, Kingston ACT 2604 -35.315726, 149.141306
CraftBeerAu_geocoded$Address[CraftBeerAu_geocoded$Venue == "The Durham"] <-  "Green Square, 2 Jardine St, Kingston ACT 2604, Australia"
CraftBeerAu_geocoded$lat[CraftBeerAu_geocoded$Venue == "The Durham"] <- -35.315726
CraftBeerAu_geocoded$lon[CraftBeerAu_geocoded$Venue == "The Durham"] <- 149.141306

# Exit - Uitgang Bar
# 406 Bridge Rd, Richmond VIC 3121 -37.819382, 145.005025
CraftBeerAu_geocoded$Address[CraftBeerAu_geocoded$Venue == "Exit Brewing"] <-  "406 Bridge Rd, Richmond VIC 3121, Australia"
CraftBeerAu_geocoded$lat[CraftBeerAu_geocoded$Venue == "Exit Brewing"] <- -37.819382
CraftBeerAu_geocoded$lon[CraftBeerAu_geocoded$Venue == "Exit Brewing"] <- 145.005025

# Going by the taplist (and the logo) GooglePlaces has selected the wrong Terminus Hotel (there's a few!) it should be - Terminus Hotel Fitzroy North 492 Queens Parade, North Fitzroy VIC 3068 -37.785139, 144.994464
CraftBeerAu_geocoded$Address[CraftBeerAu_geocoded$Venue == "The Terminus Hotel"] <-  "492 Queens Parade, North Fitzroy VIC 3068, Australia"
CraftBeerAu_geocoded$lat[CraftBeerAu_geocoded$Venue == "The Terminus Hotel"] <- -37.785139
CraftBeerAu_geocoded$lon[CraftBeerAu_geocoded$Venue == "The Terminus Hotel"] <- 144.994464

# The royal oak ended up in south africa not australia Royal Oak - SA 123 O'Connell St, North Adelaide SA 5006 -34.905231, 138.595401
CraftBeerAu_geocoded$Address[CraftBeerAu_geocoded$Venue == "The Royal Oak"] <-  "123 O'Connell St, North Adelaide SA 5006, Australia"
CraftBeerAu_geocoded$lat[CraftBeerAu_geocoded$Venue == "The Royal Oak"] <- -34.905231
CraftBeerAu_geocoded$lon[CraftBeerAu_geocoded$Venue == "The Royal Oak"] <- 138.595401



# fix the spelling of cafe (caf due to removing punc) and _ for ' 
CraftBeerAu_geocoded$Venue <- gsub("Caf", "Cafe", CraftBeerAu_geocoded$Venue)
CraftBeerAu_geocoded$Venue <- gsub("_", "'", CraftBeerAu_geocoded$Venue)

# Remove the not found
CraftBeerAu_geocoded <- CraftBeerAu_geocoded %>% filter(!lat == 0 )

# Fix data types
CraftBeerAu_geocoded$lat <- as.numeric(CraftBeerAu_geocoded$lat)
CraftBeerAu_geocoded$lon <- as.numeric(CraftBeerAu_geocoded$lon)

``` 

# Add a map (because)
```{r Map Things, include=FALSE}
attribution1 <- 'Map tiles by <a href="http://stamen.com">Stamen Design</a>, <a href="http://creativecommons.org/licenses/by/3.0">CC BY 3.0</a> &mdash; Map data &copy; <a href="http://www.openstreetmap.org/copyright">OpenStreetMap</a> | Icons made by <a href="http://www.flaticon.com/authors/nas-ztudio" title="Nas Ztudio">Nas Ztudio</a> from <a href="http://www.flaticon.com" title="Flaticon">www.flaticon.com</a> licensed by <a href="http://creativecommons.org/licenses/by/3.0/" title="Creative Commons BY 3.0" target="_blank">CC BY 3.0 </a>'  

IconCraft <- makeIcon(iconUrl = "Icons/beer-1.png",
                      iconAnchorX = 18, iconAnchorY = 12)
IconBrew <- makeIcon(iconUrl = "Icons/barrel-3.png",
                    iconAnchorX = 18, iconAnchorY = 12)
IconBar <- makeIcon(iconUrl = "Icons/beer-2.png",
                    iconAnchorX = 18, iconAnchorY = 12)

```


```{r}
# Split for layers
AuBars <- subset(CraftBeerAu_geocoded, Type == "Bar")
AuBreweries <- subset(CraftBeerAu_geocoded, Type == "Brewery")
# Also there's too many breweries! 
AuBreweries <- subset(AuBreweries, `Total votes` >= 5)


# mapping 
map <- leaflet()%>%
  setView(145.000017, -37.815943, 6) %>% 
  addTiles(urlTemplate = 'http://{s}.tile.stamen.com/toner-lite/{z}/{x}/{y}.png', 
           attribution = attribution1
  ) %>%
 addMarkers(lng = AuBreweries$lon, lat = AuBreweries$lat,
             icon = IconBrew,
             popup = paste("<b>", AuBreweries$Venue, "</b><br/>", 
                           AuBreweries$Address, "<br/> Percent Vote:", AuBreweries$`Percent Vote`),
             group = "Breweries"
  )  %>%
 addMarkers(lng = AuBars$lon, lat = AuBars$lat,
             icon = IconBar,
             popup = paste("<b>", AuBars$Venue, "</b><br/>", 
                           AuBars$Address, "<br/> Percent Vote:", AuBars$`Percent Vote`),
             group = "Bars"
  )  %>% 
  addLayersControl(
    overlayGroups = c("Breweries", "Bars"),
    options = layersControlOptions(collapsed = FALSE)
  ) 
map
```


## Limiting the Selection
Let's make this easy to start, and use my neighbourhood.
```{r}
Richmond <- subset(CraftBeerAu_geocoded, lat < -37.803399 & lat > -37.820602 & lon > 144.990518 & lon < 145.014372 )

# You can't visit Hawthorn Brewing Co (TODO: find a way to sort visitable breweries from those you can't! weirdly this brewery doesn't show in google maps)
Richmond <- Richmond[!Richmond$Venue == "Hawthorn Brewing Co", ]

# Add an ID column
Richmond$id <- rownames(Richmond)

Richmond
```


## A straight forward TSP 
```{r}
# turn the co-ords into a matrix 
coords.df <- data.frame(long=Richmond$lon, lat=Richmond$lat)
coords.mx <- as.matrix(coords.df)

# Compute great-circle distance matrix
dist.mx <- spDists(coords.mx, longlat=TRUE)
dist.mx

# TSP object
tsp.ins <- tsp_instance(coords.mx, dist.mx )
tsp.ins

# Solve 
tour <- run_solver(tsp.ins, method="2-opt")
tour

# Compare Solvers
tours = sapply(c("nn", "cheapest_insertion", "arbitrary_insertion", "2-opt"), function(solver) {
  list(solver = run_solver(tsp.ins, method = solver))
})
tours
# 2-opt is pretty good!

# Permutation Vector 
tour_order <- as.integer(tour)

# Plot
autoplot(tsp.ins, tour)

# reorder
Richmond_tour <- Richmond[match(tour_order, Richmond$id),]
Richmond_tour

```



## Map it
```{r}
# On a Map

map <- leaflet()%>%
  setView(145.000017, -37.815943, 14) %>% 
  addTiles(urlTemplate = 'http://{s}.tile.stamen.com/toner-lite/{z}/{x}/{y}.png', 
           attribution = attribution1
  ) %>%
 addMarkers(lng = Richmond_tour$lon, lat = Richmond_tour$lat,
             icon = IconCraft,
             popup = paste("<b>", Richmond_tour$Venue, "</b><br/>", Richmond_tour$Address),
             group = "Location"
  ) %>% 
  addPolylines(lng = Richmond_tour$lon, lat = Richmond_tour$lat)
map

```


# Apply the GoogleDirections API 
We can't fly between venues though, so back to google
```{r}
library(dplyr)
library(gmapsdistance)

Richmond_dist <- Richmond %>% 
  select (Venue, lat, lon) %>% 
  mutate(latlon = paste(lat, lon, sep ="+")) 

results <- gmapsdistance(origin = Richmond_dist$latlon, 
                        destination = Richmond_dist$latlon, 
                        mode = "walking", 
                        departure = 1514742000,
                        key = DirectionsMatrixKey)

#Alternate https://rgeomatic.hypotheses.org/854
# https://www.r-bloggers.com/introducing-the-nominatim-geocoding-package/

library(nominatim)
osm_chk <- osm_search("Pirate Life in Australia", limit=20)

```
 

# Then Solve Again

```{r}
# time matrix
timematrix <- data.frame(results$Time)
timematrix <- timematrix[,-1]
time.mx <- as.matrix(timematrix)
colnames(time.mx) <- NULL
rownames(time.mx) <- NULL
isSymmetric.matrix(time.mx)
# The time matrix is not symmetric - weird!!

# so distance then?
distancematrix <- data.frame(results$Distance)
distancematrix <- distancematrix[,-1]
distance.mx <- as.matrix(distancematrix)
colnames(distance.mx) <- NULL
rownames(distance.mx) <- NULL
# The distance matrix is not symmetric - either, so manually change the problem one 
# TODO why???
distance.mx <- replace(distance.mx, distance.mx == 2721, 2719)
isSymmetric.matrix(distance.mx)

# setup tsp
tsp.ins.dist <- tsp_instance(coords.mx, distance.mx )
tsp.ins.dist

# Solve 
tour.dist <- run_solver(tsp.ins.dist, method="2-opt")
tour.dist


# Compare Solvers
tours <- sapply(c("nn", "cheapest_insertion", "arbitrary_insertion", "2-opt"), function(solver) {
  list(solver = run_solver(tsp.ins.dist, method = solver))
})
tours
# 2-opt is pretty good!

# Permutation Vector 
tour_order_dist <- as.integer(tour.dist)
tour_order
tour_order_dist
# so the same as flying basically!

# Plot
autoplot(tsp.ins.dist, tour.dist)

# reorder
Richmond_tour_dist <- Richmond[match(tour_order_dist, Richmond$id),]
Richmond_tour_dist
Richmond_tour

```


```{r}

# matrix not symmetric is concerning 
# maybe use googleway again as it includes the path, extract the distance combos and popualate matrix or ..

# a diy matrix api function - not working correctly though  :(

library(RCurl)
library(RJSONIO)
library(plyr)


urlm <- function(origin, destination, return.call = "json") {
  rootm <- "http://maps.googleapis.com/maps/api/distancematrix/"
  um <- paste(root, return.call, "?origins=", origin, "&destinations=", destination, "&mode=walking&units=metric&language=EN&sensor=false&key=", key, sep = "")
  return(URLencode(um))
}


walk <- function(origin, destination,verbose=FALSE) {
 if(verbose) cat(origin,destinaiton,"\n")
 u <- urlm(origin,destination)
 doc <- getURL(u)
 x <- fromJSON(doc,simplify = FALSE)
 if(x$status=="OK") {
  dist <- x$rows[[1]]$elements[[1]]$distance$text
  return(c(dist))
 } else {
  return(c(NA))
 }
}

Rorigin <- Richmond_dist$latlon
Rdestination <- Richmond_dist$latlon 

diymatrix <- ldply(Rorigin, Rdestination, function(x) walk(x))

```


# Plot Route in Leaflet

```{r}
# maybe go back to the googleway package??
```

# Go Huge
Get all the directions time for those in each city (pick coords or limit to best of best), set a max time and number and solve again. 
```{r}

```



```{r, eval=FALSE, include=FALSE}

### Useful things from along the way
# https://rpubs.com/leehbi/tour
# http://mortada.net/the-traveling-tesla-salesman-part-2.html
# https://developers.google.com/optimization/routing/tsp/tsp
# https://github.com/berndbischl/tspmeta
# https://cran.r-project.org/web/packages/TSP/vignettes/TSP.pdf
# http://berndbischl.github.io/tspmeta/man/
# https://operatiology.wordpress.com/2014/05/31/tsp-with-latitudelongitude-coordinate-input-in-r/


# Using this function from: https://rpubs.com/walkerke/points_to_line
library(sp)
library(maptools)

points_to_line <- function(data, long, lat, id_field = NULL, sort_field = NULL) {
  
  # Convert to SpatialPointsDataFrame
  coordinates(data) <- c(long, lat)
  
  # If there is a sort field...
  if (!is.null(sort_field)) {
    if (!is.null(id_field)) {
      data <- data[order(data[[id_field]], data[[sort_field]]), ]
    } else {
      data <- data[order(data[[sort_field]]), ]
    }
  }
  
  # If there is only one path...
  if (is.null(id_field)) {
    
    lines <- SpatialLines(list(Lines(list(Line(data)), "id")))
    
    return(lines)
    
    # Now, if we have multiple lines...
  } else if (!is.null(id_field)) {  
    
    # Split into a list by ID field
    paths <- sp::split(data, data[[id_field]])
    
    sp_lines <- SpatialLines(list(Lines(list(Line(paths[[1]])), "line1")))
    
    # I like for loops, what can I say...
    for (p in 2:length(paths)) {
      id <- paste0("line", as.character(p))
      l <- SpatialLines(list(Lines(list(Line(paths[[p]])), id)))
      sp_lines <- spRbind(sp_lines, l)
    }
    
    return(sp_lines)
  }
}

library(leaflet)

dat <- read.csv('shapes.txt')

v_lines <- points_to_line(data = dat, 
                          long = "shape_pt_lon", 
                          lat = "shape_pt_lat", 
                          id_field = "shape_id", 
                          sort_field = "shape_pt_sequence")

leaflet(data = v_lines) %>%
  addTiles() %>%
  addPolylines()

```


